VIP-193: Committee-Based POA

### 2019-11-21 article.tex
fix num

\subsection{Double-Spending Attack}
The main goal of introducing the committee mechanism is to make it more difficult for adversaries to cause inconsistency. Perhaps the most damaging of such attacks is the double-spending attacks~(DSAs)~\cite{Sat08} where adversaries are allowed to take control of a few consecutive consensus rounds such that they can produce two parallel branches to launch a DSA. Here we are going to infer a lower bound for the probability of launching a $k$-block DSA.

@@

Now let us consider the worse-case scenario when a malicious leader is selected to generate the block in the last epoch from which the random beacon for the current epoch is computed. The best he can do is to try all the combinations of $d$ valid signatures he receives from the committee members to search for a combination that will result in $k$ consecutive rounds in which leaders are all malicious in the next epoch. Therefore, we can compute a lower bound for the probability of launching a $k$-block DSA as:

@@

\begin{table}[H]
    \centering
    \begin{tabular}{|c|C{2.5cm}|C{2.5cm}|}
        \hline
        $N = 101$, $f=33$ & $k=5$ & $k=10$ \\
        \hline\hline
        $d=5$ & $1.57\times10^{-6}$ & $4.38\times10^{-14}$ \\
        \hline
        $d=10$ & $6.04\times10^{-8}$ & $4.56\times10^{-19}$ \\
        \hline
    \end{tabular}
    \vspace{2ex}
    \caption{Examples of probabilities $F(p_\epsilon,d,f)^k$. Here we compute $p_\epsilon=1.5\cdot d/N$ and $c=\lfloor1.5\cdot d\rfloor$.}
    \label{tab:dsa-prob}
\end{table}

>>>>

\subsection{Double-Spending Attack}
The main goal of introducing the committee mechanism is to make it more difficult for adversaries to cause inconsistency. Perhaps the most damaging of such attacks is the double-spending attacks~(DSAs)~\cite{Sat08} where adversaries are allowed to take control of a few consecutive consensus rounds such that they can produce two parallel branches to launch a DSA. Here we are going to infer a upper bound for the probability of launching a $k$-block DSA.

@@

Now let us consider the worse-case scenario when a malicious leader is selected to generate the block in the last epoch from which the random beacon for the current epoch is computed. The best he can do is to try all the combinations of $d$ valid signatures he receives from the committee members to search for a combination that will result in $k$ consecutive rounds in which leaders are all malicious in the next epoch. Therefore, we can compute a upper bound for the probability of launching a $k$-block DSA as:

@@

\begin{table}[H]
    \centering
    \begin{tabular}{|c|C{2.5cm}|C{2.5cm}|}
        \hline
        $N = 101$, $f=33$ & $k=5$ & $k=10$ \\
        \hline\hline
        $d=5$ & $1.86\times10^{-7}$ & $1.65\times10^{-15}$ \\
        \hline
        $d=10$ & $2.78\times10^{-8}$ & $1.17\times10^{-19}$ \\
        \hline
    \end{tabular}
    \vspace{2ex}
    \caption{Examples of probabilities $F(p_\epsilon,d,f)^k$. Here we compute $p_\epsilon=1.5\cdot d/N$ and $c=\lfloor1.5\cdot d\rfloor$.}
    \label{tab:dsa-prob}
\end{table}
